Boosting, Sparsity, and Conditional Gradient: A Tutorial

### 2014-04-01 arXiv/sparsity-result.tex
added some defs; added a couple comments to sparsity result section

% give convergence theorem for boosted version
Algorithm~\ref{alg:boosted-comid} enjoys the following primal-dual convergence rate:
\begin{theorem}
Define the \emph{duality gap} $\Delta_T$ as
\[ \Delta_T \eqdef \sup_{v \in \Conv(S)} f(v, w_T) - \inf_{w \in \W} f(v_T, w). \]
Suppose that $\psi$ is $\rho_0$-strongly convex with 
respect to a norm $\|\cdot\|$, and that $h$ is $\rho$-strongly 
convex with respect to the same norm. Suppose that 
$\|\nabla g_t\|_* \leq r$ for all $t$. Then, defining 
$A_t \eqdef \sum_{s=1}^T \alpha_s$ as before, we have
\[ \Delta_T \leq \frac{1}{A_T} \psi(w_T) + \frac{r^2}{2A_T} \sum_{t=1}^T \frac{\alpha_t^2}{\rho_0 + \rho A_t}. \]
In addition, $v_T$ is $(S, T)$-sparse.
\end{theorem}
%\begin{remark}
%If $f$ is a continuously differentiable function, the compactness of $S$ 
%guarantees that $\sup_{v \in S} \|\nabla g(v, w)\|_*$ is finite for each 
%$w$. 
%\end{remark}
\begin{corollary}
Suppose that $\psi \equiv 0$ and $\rho > 0$, and set $\alpha_t = t$. Then 
\[ \Delta_T \leq \frac{2r^2}{\rho (T+1)}. \]
\end{corollary}

\begin{corollary}
Suppose that $\rho_0 > 0$ and set $\alpha_t = 2/\sqrt{T}$. Then
\[ \Delta_T \leq \frac{1}{\sqrt{T}} \left[ \psi(w_T) + \frac{2r^2\log(T+1)}{\rho_0} \right]. \]
\end{corollary}

>>>>

% give convergence theorem for boosted version
Algorithm~\ref{alg:boosted-comid} enjoys the following primal-dual convergence rate:\fTBD{JHH: did you mean do use $v_{T}$ and $w_{T}$ here, or should those be $v^{*}$ and $w^{*}$?}
\begin{theorem}
Define the \emph{duality gap} $\Delta_T$ as
\[ \Delta_T \eqdef \sup_{v \in \Conv(S)} f(v, w_T) - \inf_{w \in \W} f(v_T, w). \]
Suppose that $\psi$ is $\rho_0$-strongly convex with 
respect to a norm $\|\cdot\|$, and that $h$ is $\rho$-strongly 
convex with respect to the same norm. Suppose that 
$\|\nabla g_t\|_* \leq r$ for all $t$. Then, defining 
$A_t \eqdef \sum_{s=1}^T \alpha_s$ as before, we have
\[ \Delta_T \leq \frac{1}{A_T} \psi(w_T) + \frac{r^2}{2A_T} \sum_{t=1}^T \frac{\alpha_t^2}{\rho_0 + \rho A_t}. \]
In addition, $v_T$ is $(S, T)$-sparse.
\end{theorem}
%\begin{remark}
%If $f$ is a continuously differentiable function, the compactness of $S$ 
%guarantees that $\sup_{v \in S} \|\nabla g(v, w)\|_*$ is finite for each 
%$w$. 
%\end{remark}
\begin{corollary}
Suppose that $\psi \equiv 0$ and $\rho > 0$, and set $\alpha_t = t$. Then 
\[ \Delta_T \leq \frac{2r^2}{\rho (T+1)}. \]
\end{corollary}

\begin{corollary} \label{cor:duality-cor-2} % XXX: should come up with a better label for this
Suppose that $\rho_0 > 0$ and set $\alpha_t = 2/\sqrt{T}$. Then
\[ \Delta_T \leq \frac{1}{\sqrt{T}} \left[ \psi(w_T) + \frac{2r^2\log(T+1)}{\rho_0} \right]. \]
\end{corollary}
